Wavelength convergence of the ${\mathrm{\:E}\times\mathrm{B}}$ staircase pattern in flux tube simulations of ion temperature gradient driven turbulence

### 2023-02-26 briefcommunicaton/briefcommunication.tex
#37: Changed binormal heatflux plot
#37: New plots in paper

% \increasecounter{fig}{1}

\includegraphicsTwoCol{{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_wexb_comparison}.pdf}{
	Comparison of shearing rate $\omega_{\mathrm{\:E \times B}}$ for radial increased box sizes. The staircase structure got 
	shifted for better visibility.
}{fig:wexb-1-2-3-4x1-stable-comparison}{}

@@

\includegraphicsOneCol{{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_wexb_selection}.pdf}{
	Stablized shearing rate $\omega_{\mathrm{\:E \times B}}$ for boxsize 3$\times$3. \textcolor{red}{Add $1\times1$, $2\times2$!}
}{fig:wexb-3x3-stable}

>>>>

\includegraphicsTwoCol{{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1-1.5-2-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison}.pdf}{
	Comparison of shearing rate $\omega_{\mathrm{\:E \times B}}$ for radial increased box sizes. The staircase structure got 
	shifted for better visibility.
}{fig:wexb-1-2-3-4x1-stable-comparison}{}

@@

\includegraphicsOneCol{{Comparison/Boxsize/S6_rlt6.0_boxsize3x1-1.5-2.5-3-5_Ns16_Nvpar48_Nmu9_eflux_comparison}.pdf}{
	Time traces of the heat conduction coefficient $\chi$ for $R/L_T = 6.0$ for binormal increased box sizes
}{fig:eflux-1x1-2x2-3x3-comparison}

%\includegraphicsOneCol{{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_wexb_selection}.pdf}{
%	Stablized shearing rate $\omega_{\mathrm{\:E \times B}}$ for boxsize 3$\times$3. \textcolor{red}{Add $1\times1$, $2\times2$!}
%}{fig:wexb-3x3-stable}
